---
title: "zzov_12batch"
author: "yuyi"
date: "2021/12/20"
output: html_document
---

```{r}
rm(list = ls())

options(stringsAsFactors = F)
source("D:/datamining_library_ge.R")
source("D:/library_yu.R")

library(DMwR2)
library(openxlsx)
library(ggpubr)
df <- ge.readtable(paste0("./CAC20211125qianlj_ZZOV_plasma_TMT16plex_60min_b1__Proteins.txt"))
df1 <- df[df$Protein.FDR.Confidence..Combined=="High",]
df1 <- df1[!grepl(";",df1$Accession),]
df1 <- df1[!grepl("CON_",df1$Accession),]
df2 <- df1[,grep("Ratio|Grouped...F[1-9]*..126",names(df1))]

# name=str_extract(names(df2),"[F][0-9]*..1[0-9][0-9][A-Z]*")
name=str_extract(names(df2),"F[0-9]*..[0-9A-Z]*")
name= gsub("\\.\\.","_",name)
name= gsub("F","b",name)
names(df2)=name

df1$Gene.Symbol[which(df1$`Gene.Symbol`=="")]=NA
df2 <- as.data.frame(df2)
row.names(df2)=paste0(df1$Accession,"_",as.character(sapply(df1$`Gene.Symbol`, function(x){str_split(x,";")[[1]][1]})))





df3 <- df2[,-grep("126",names(df2))]


#pool
pool<- df2[,grep("126",names(df2))]


NA_threshold_table(df3)
NA_threshold_table(pool)



df3_7 <- df3[apply(df3,1, function(x){sum(is.na(x))/ncol(df3)})<0.7,]
# df5_7[is.na(df5_7)]<-min(df5_7)*0.5


pool_7 <- pool[apply(pool,1, function(x){sum(is.na(x))/ncol(pool)})<0.7,]
# pool_7[is.na(pool_7)]<-min(pool_7)*0.5

write.csv(df5,"matrix.csv")
write.csv(df3_7,"12batch_matrix0.7.csv")

```




```{r}
info <- read_excel("./20211207ZZOV_plasmaValidation_batchDesign.xlsx",sheet = 3)

Input1 <- read_csv("./20211220_ZZOVplasma12batch_matrix0.7.csv")
name=Input1$swissprotID
Input1=Input1[,-1]
rownames(Input1)= name

Input2 <- read_csv("./BatchFree_batch_MS2021-12-20.csv")
Input2=Input2[,-1]
rownames(Input2)= name

Input3 <- read_csv("./BatchFree_batch2021-12-20.csv")
Input3=Input3[,-1]
rownames(Input3)= name



library(ggthemes)
set.seed(10)
TMTbatch<- info$TMTbatch[match(colnames(Input1),info$name)]
TMTbatch2<-str_extract(TMTbatch,"[0-9]*[0-9]")
TMTbatch2<-as.numeric(TMTbatch2)


ge.plot.pca2(Input3,TMTbatch2,title="TMT_3",width=12,height=8)


caabatch<- info$matrix[match(colnames(Input1),info$name)]

ge.plot.pca(Input3,caabatch,title="CAA_3",width=12,height=8)


label1<- info$label1[match(colnames(Input1),info$name)]

ge.plot.pca(Input3,label1,title="nbh_3",width=12,height=8)






library(dplyr)


id.rep<- info$SampleName[match(colnames(Input3),info$name)]
rep<-Input3
colnames(rep)<-id.rep
repB <- names(rep)[grepl("_rep", names(rep))]
type<-gsub('_rep', '', repB)

############################rep cv
# fivenum(tmp)
sum.cv <-c()
mean_value <- rownames(rep)
mid.cv <-c()
type<-c()
# i=repB[1]
for (i in repB) {
  repa <- str_split(i,"_rep")[[1]][1]
  tmp <- rep[,which(names(rep) %in% c(repa,i))]
  if (length(tmp)==2){
  type<-c(type,repa)
  tmp.cv <- apply(tmp, 1 , function(x){sd(x,na.rm = T)/mean(x,na.rm =T)}) 
  tmp.mean <- apply(tmp, 1 , mean,na.rm=T)  
  
  sum.cv <- c(sum.cv,tmp.cv)
  mean_value <-cbind.data.frame(mean_value,tmp.mean)
  
  mid.tmp <- median(tmp.cv,na.rm = T)
  mid.cv <- c(mid.cv,mid.tmp)
  }else{return}
  }
mean_value <- mean_value[,-1]
names(mean_value) <- repB


 df.cv <- data.frame(cv=sum.cv,sample=rep("rep",each=nrow(rep)))

df.cv <- df.cv[!is.na(df.cv$cv),]

n_fun <- function(x){
  return(data.frame(y = max(x)+0.1, label = paste0("median =",round(median(x),3))))
}

#plot violin
p<-ggplot(df.cv, aes(x = sample, y=cv,color=sample)) + 
  geom_violin(trim=FALSE)+
  scale_fill_manual(values=brewer.pal(12,"Set3")[c(1:10)])+
  geom_boxplot(width=0.1)+
  theme(legend.direction = 'horizontal',legend.position = 'top',panel.grid.major =element_blank(), panel.grid.minor = element_blank(),panel.background = element_blank(),axis.line = element_line(colour = "black"))+
 
   theme(axis.text = element_text(size = 16,colour = "black"),text = element_text(size = 30,colour = "black"))+
  theme(axis.text.x = element_text( hjust = 1,angle = 45))+
  theme(legend.position = "none")+
  stat_summary(fun.data =n_fun, geom="text")
ggsave("CV_all.pdf",plot =p ,device = NULL,width = 8, height = 8)



